Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-08-04 writing/DraftExposurePaper/DraftExposurePaper.Rmd
Add comparison for orleans, fulton, floyd, and charleston counties

>>>>

Compare data from `countyweather` and NLDAS-2 data for Orleans perish by storm:

```{r}
check_dates <- dplyr::select(closest_dist, -storm_dist) %>%
        dplyr::mutate(closest_date = ymd(closest_date)) %>%
        dplyr::rename(day_0 = closest_date) %>%
        dplyr::mutate(fips = as.integer(fips),
                      day_0 = day_0 + days(0),
                      day_b1 = day_0 - days(1),
                      day_b2 = day_0 - days(2),
                      day_a1 = day_0 + days(1),
                      day_a2 = day_0 + days(2),
                      day_a3 = day_0 + days(3)) %>%
        dplyr::select(storm_id, fips, day_b2, day_b1,
                      day_0, day_a1, day_a2, day_a3) %>%
        tidyr::gather(key = lag, value = day, -storm_id, -fips) %>%
        dplyr::rename(date = day) %>%
        dplyr::filter(fips == "22071") %>%
        dplyr::mutate(fips = as.character(fips))
        #dplyr::mutate(day = as.numeric(format(day, "%Y%m%d")))

fips <- "22071"
# I've commented this out because we're saving the data, so we only need
# to run it once.
# county_timeseries(fips, percent_coverage = 0,
#                   date_min = "1988-01-01", date_max = "2011-12-31",
#                   var = "PRCP",
#                   out_directory = "orleans_data/")

# miami_dade_dir <- "~/Documents/hurricaneexposure/writing/DraftExposurePaper/dade_data/"
orleans_dir <- "orleans_data/"
orleans_weather <- readRDS(paste0(orleans_dir, fips, ".rds"))

#orleans_weather <- orleans_weather$averaged %>%
#        filter(date %in% seq(from = as.Date("1988-01-01"), to = as.Date("2011-12-31"), by = 1))

orleans_weather <- orleans_weather %>%
        filter(date %in% seq(from = as.Date("1988-01-01"), to = as.Date("2011-12-31"), by = 1))

orleans_weather$fips <- fips
orleans_weather <- as.data.frame(orleans_weather)

orleans_weather <- orleans_weather %>%
        dplyr::filter(date %in% all_dates) %>%
        dplyr::right_join(data.table(check_dates),
                          by = c("fips" = "fips", "date" = "date")) %>%
        dplyr::filter(!is.na(prcp)) %>%
        dplyr::arrange(storm_id, fips) %>%
        dplyr::mutate(fips = as.integer(fips)) %>%
        dplyr::mutate(fips = sprintf("%05d", fips),
                      lag = gsub("day_", "", lag),
                      lag = gsub("b", "-", lag),
                      lag = gsub("a", "", lag),
                      lag = as.numeric(lag))

orleans_rain <- countyweather_rain(counties = fips, county_weather = orleans_weather,
                                 start_year = 1988, end_year = 2011,
                                 rain_limit = 0, dist_limit = 2000)
orleans_plot <- ggplot(orleans_rain, aes(x = cw_precip, y = tot_precip)) +
        geom_hline(aes(yintercept = 75), color = "lightgray") +
        geom_vline(aes(xintercept = 75), color = "lightgray") +
        geom_abline(aes(intercept = 0, slope = 1), color = "gray", alpha = 0.5) +
        # geom_point(aes(size = prcp_reporting), alpha = 0.2) +
        geom_point(alpha = 0.5) +
        # geom_text(aes(x = monitor_rain + 100, label = storm_id)) +
        xlim(c(0, 275)) + ylim(c(0, 275)) +
        theme_few() +
        scale_size_continuous(guide = "none") +
        xlab("Rainfall (mm) based on \naveraged county monitors") +
        ylab("Rainfall (mm) based on \nNLDAS-2 county data") +
        ggtitle("Monitor versus NLDAS rainfall estimates \nfor Orleans perish, LA, by storm")

orleans_plot
```

Compare data from `countyweather` and NLDAS-2 data for Charleston county by storm:

```{r}
check_dates <- dplyr::select(closest_dist, -storm_dist) %>%
        dplyr::mutate(closest_date = ymd(closest_date)) %>%
        dplyr::rename(day_0 = closest_date) %>%
        dplyr::mutate(fips = as.integer(fips),
                      day_0 = day_0 + days(0),
                      day_b1 = day_0 - days(1),
                      day_b2 = day_0 - days(2),
                      day_a1 = day_0 + days(1),
                      day_a2 = day_0 + days(2),
                      day_a3 = day_0 + days(3)) %>%
        dplyr::select(storm_id, fips, day_b2, day_b1,
                      day_0, day_a1, day_a2, day_a3) %>%
        tidyr::gather(key = lag, value = day, -storm_id, -fips) %>%
        dplyr::rename(date = day) %>%
        dplyr::filter(fips == "45019") %>%
        dplyr::mutate(fips = as.character(fips))
        #dplyr::mutate(day = as.numeric(format(day, "%Y%m%d")))

fips <- "45019"
# I've commented this out because we're saving the data, so we only need
# to run it once.
# county_timeseries(fips, percent_coverage = 0,
#                   date_min = "1988-01-01", date_max = "2011-12-31",
#                   var = "PRCP",
#                   out_directory = "charleston_data/")

# miami_dade_dir <- "~/Documents/hurricaneexposure/writing/DraftExposurePaper/dade_data/"
charleston_dir <- "charleston_data/"
charleston_weather <- readRDS(paste0(charleston_dir, fips, ".rds"))

#orleans_weather <- orleans_weather$averaged %>%
#        filter(date %in% seq(from = as.Date("1988-01-01"), to = as.Date("2011-12-31"), by = 1))

charleston_weather <- charleston_weather %>%
        filter(date %in% seq(from = as.Date("1988-01-01"), to = as.Date("2011-12-31"), by = 1))

charleston_weather$fips <- fips
charleston_weather <- as.data.frame(charleston_weather)

charleston_weather <- charleston_weather %>%
        dplyr::filter(date %in% all_dates) %>%
        dplyr::right_join(data.table(check_dates),
                          by = c("fips" = "fips", "date" = "date")) %>%
        dplyr::filter(!is.na(prcp)) %>%
        dplyr::arrange(storm_id, fips) %>%
        dplyr::mutate(fips = as.integer(fips)) %>%
        dplyr::mutate(fips = sprintf("%05d", fips),
                      lag = gsub("day_", "", lag),
                      lag = gsub("b", "-", lag),
                      lag = gsub("a", "", lag),
                      lag = as.numeric(lag))

charleston_rain <- countyweather_rain(counties = fips, county_weather = charleston_weather,
                                 start_year = 1988, end_year = 2011,
                                 rain_limit = 0, dist_limit = 2000)
charleston_plot <- ggplot(charleston_rain, aes(x = cw_precip, y = tot_precip)) +
        geom_hline(aes(yintercept = 75), color = "lightgray") +
        geom_vline(aes(xintercept = 75), color = "lightgray") +
        geom_abline(aes(intercept = 0, slope = 1), color = "gray", alpha = 0.5) +
        # geom_point(aes(size = prcp_reporting), alpha = 0.2) +
        geom_point(alpha = 0.5) +
        # geom_text(aes(x = monitor_rain + 100, label = storm_id)) +
        xlim(c(0, 275)) + ylim(c(0, 275)) +
        theme_few() +
        scale_size_continuous(guide = "none") +
        xlab("Rainfall (mm) based on \naveraged county monitors") +
        ylab("Rainfall (mm) based on \nNLDAS-2 county data") +
        ggtitle("Monitor versus NLDAS rainfall estimates \nfor Charleston county, SC, by storm")

charleston_plot
```

Compare data from `countyweather` and NLDAS-2 data for Floyd county by storm:

```{r}
check_dates <- dplyr::select(closest_dist, -storm_dist) %>%
        dplyr::mutate(closest_date = ymd(closest_date)) %>%
        dplyr::rename(day_0 = closest_date) %>%
        dplyr::mutate(fips = as.integer(fips),
                      day_0 = day_0 + days(0),
                      day_b1 = day_0 - days(1),
                      day_b2 = day_0 - days(2),
                      day_a1 = day_0 + days(1),
                      day_a2 = day_0 + days(2),
                      day_a3 = day_0 + days(3)) %>%
        dplyr::select(storm_id, fips, day_b2, day_b1,
                      day_0, day_a1, day_a2, day_a3) %>%
        tidyr::gather(key = lag, value = day, -storm_id, -fips) %>%
        dplyr::rename(date = day) %>%
        dplyr::filter(fips == "51063") %>%
        dplyr::mutate(fips = as.character(fips))
        #dplyr::mutate(day = as.numeric(format(day, "%Y%m%d")))

fips <- "51063"
# I've commented this out because we're saving the data, so we only need
# to run it once.
# county_timeseries(fips, percent_coverage = 0,
#                   date_min = "1988-01-01", date_max = "2011-12-31",
#                   var = "PRCP",
#                   out_directory = "floyd_data/")

floyd_dir <- "floyd_data/"
floyd_weather <- readRDS(paste0(floyd_dir, fips, ".rds"))

#orleans_weather <- orleans_weather$averaged %>%
#        filter(date %in% seq(from = as.Date("1988-01-01"), to = as.Date("2011-12-31"), by = 1))

floyd_weather <- floyd_weather %>%
        filter(date %in% seq(from = as.Date("1988-01-01"), to = as.Date("2011-12-31"), by = 1))

floyd_weather$fips <- fips
floyd_weather <- as.data.frame(floyd_weather)

floyd_weather <- floyd_weather %>%
        dplyr::filter(date %in% all_dates) %>%
        dplyr::right_join(data.table(check_dates),
                          by = c("fips" = "fips", "date" = "date")) %>%
        dplyr::filter(!is.na(prcp)) %>%
        dplyr::arrange(storm_id, fips) %>%
        dplyr::mutate(fips = as.integer(fips)) %>%
        dplyr::mutate(fips = sprintf("%05d", fips),
                      lag = gsub("day_", "", lag),
                      lag = gsub("b", "-", lag),
                      lag = gsub("a", "", lag),
                      lag = as.numeric(lag))

floyd_rain <- countyweather_rain(counties = fips, county_weather = floyd_weather,
                                 start_year = 1988, end_year = 2011,
                                 rain_limit = 0, dist_limit = 2000)
floyd_plot <- ggplot(floyd_rain, aes(x = cw_precip, y = tot_precip)) +
        geom_hline(aes(yintercept = 75), color = "lightgray") +
        geom_vline(aes(xintercept = 75), color = "lightgray") +
        geom_abline(aes(intercept = 0, slope = 1), color = "gray", alpha = 0.5) +
        # geom_point(aes(size = prcp_reporting), alpha = 0.2) +
        geom_point(alpha = 0.5) +
        # geom_text(aes(x = monitor_rain + 100, label = storm_id)) +
        xlim(c(0, 275)) + ylim(c(0, 275)) +
        theme_few() +
        scale_size_continuous(guide = "none") +
        xlab("Rainfall (mm) based on \naveraged county monitors") +
        ylab("Rainfall (mm) based on \nNLDAS-2 county data") +
        ggtitle("Monitor versus NLDAS rainfall estimates \nfor Floyd county, VA, by storm")

floyd_plot
```

Compare data from `countyweather` and NLDAS-2 data for Fulton county by storm:

```{r}
check_dates <- dplyr::select(closest_dist, -storm_dist) %>%
        dplyr::mutate(closest_date = ymd(closest_date)) %>%
        dplyr::rename(day_0 = closest_date) %>%
        dplyr::mutate(fips = as.integer(fips),
                      day_0 = day_0 + days(0),
                      day_b1 = day_0 - days(1),
                      day_b2 = day_0 - days(2),
                      day_a1 = day_0 + days(1),
                      day_a2 = day_0 + days(2),
                      day_a3 = day_0 + days(3)) %>%
        dplyr::select(storm_id, fips, day_b2, day_b1,
                      day_0, day_a1, day_a2, day_a3) %>%
        tidyr::gather(key = lag, value = day, -storm_id, -fips) %>%
        dplyr::rename(date = day) %>%
        dplyr::filter(fips == "13121") %>%
        dplyr::mutate(fips = as.character(fips))
        #dplyr::mutate(day = as.numeric(format(day, "%Y%m%d")))

fips <- "13121"
# I've commented this out because we're saving the data, so we only need
# to run it once.
# county_timeseries(fips, percent_coverage = 0,
#                   date_min = "1988-01-01", date_max = "2011-12-31",
#                   var = "PRCP",
#                   out_directory = "fulton_data/")

fulton_dir <- "fulton_data/"
fulton_weather <- readRDS(paste0(fulton_dir, fips, ".rds"))

#orleans_weather <- orleans_weather$averaged %>%
#        filter(date %in% seq(from = as.Date("1988-01-01"), to = as.Date("2011-12-31"), by = 1))

fulton_weather <- fulton_weather %>%
        filter(date %in% seq(from = as.Date("1988-01-01"), to = as.Date("2011-12-31"), by = 1))

fulton_weather$fips <- fips
fulton_weather <- as.data.frame(fulton_weather)

fulton_weather <- fulton_weather %>%
        dplyr::filter(date %in% all_dates) %>%
        dplyr::right_join(data.table(check_dates),
                          by = c("fips" = "fips", "date" = "date")) %>%
        dplyr::filter(!is.na(prcp)) %>%
        dplyr::arrange(storm_id, fips) %>%
        dplyr::mutate(fips = as.integer(fips)) %>%
        dplyr::mutate(fips = sprintf("%05d", fips),
                      lag = gsub("day_", "", lag),
                      lag = gsub("b", "-", lag),
                      lag = gsub("a", "", lag),
                      lag = as.numeric(lag))

fulton_rain <- countyweather_rain(counties = fips, county_weather = fulton_weather,
                                 start_year = 1988, end_year = 2011,
                                 rain_limit = 0, dist_limit = 2000)
fulton_plot <- ggplot(fulton_rain, aes(x = cw_precip, y = tot_precip)) +
        geom_hline(aes(yintercept = 75), color = "lightgray") +
        geom_vline(aes(xintercept = 75), color = "lightgray") +
        geom_abline(aes(intercept = 0, slope = 1), color = "gray", alpha = 0.5) +
        # geom_point(aes(size = prcp_reporting), alpha = 0.2) +
        geom_point(alpha = 0.5) +
        # geom_text(aes(x = monitor_rain + 100, label = storm_id)) +
        xlim(c(0, 275)) + ylim(c(0, 275)) +
        theme_few() +
        scale_size_continuous(guide = "none") +
        xlab("Rainfall (mm) based on \naveraged county monitors") +
        ylab("Rainfall (mm) based on \nNLDAS-2 county data") +
        ggtitle("Monitor versus NLDAS rainfall estimates \nfor Fulton county, GA, by storm")

fulton_plot
```
